Investigating Trends of Absences in Toronto City Council Attendance between 2022 to 2026

### 2024-09-26 paper/paper.qmd
Updated llm usage chat history & filled in any remaining gaps in the report

---
title: "Investigating Trends of Absences in Toronto City Council Attendance between 2022 to 2026"
subtitle: "Determining the Ideal Meeting Types and Months for the 2022-2026 Term"
author: 
  - Wendy Yuan
thanks: "GitHub repo link: https://github.com/kiwindyy/CityCouncilAttendance"
date: "27 September 2024"
date-format: long
abstract: "This paper looks at trends in absences for Toronto City Council members using data from Open Data Toronto (@toronto-city-council-attendance). The data was used to observe which members had the most absences, absences trends over the years, and what meeting types had the most absences. It was found that evening meetings saw the most absences and absences are predicted to see an increase over the years. Through identifying trends of absences, we can help minimize the number of absences by ___ members which is important as when City Council members are elected, they are expected to attend meetings to voice the population’s opinions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The data analysis focuses on examining patterns in the data for various causes of absences. It was found that evening meetings experienced the most absences and the trend over the years shows that absences are likely to increase in 2022. Additionally, ___ members were found to have the most absences. Rather than blaming individuals for absences, understanding these patterns allows for future targeted meeting scheduling to minimize absences. This ensures that elected officials are present to represent the voices of the general.

@@

After importing the data into R (@citeR) using the Open Data Toronto package (@OpenDataToronto), it is cleaned to keep only key variables of interest and make it easier for data analysis in Section 3. To clean the data and produce graphs with the data, the following packages in R (@citeR) were used: tidyverse (@tidyverse), dplyr (@dplyr), lubridate (@lubridate), knitr (@knitr), readr (@readr) and ggplot2 (@ggplot2).

@@

In @fig-session-member the taller the bar is the more absences that City Council member has had while the opposite is true, the lower the bar the fewer absences. It can be seen that some members rarely miss sessions such as ___ while others, such as ___, have missed notably more. Thus, @fig-session-member shows a general idea of individual absences, this graph makes it difficult to follow trends in the future.

@@

@fig-session-member from Section 3 laid out the information about the absences of each Toronto City Council member. It can be seen that __ has the highest absences, while __ has the lowest. The variation between members could be problematic especially when the council member fails to represent the population. Additionally, it could suggest differences in engagement, personal schedules, or emergency circumstances. Determining those with the most absences allows steps to be taken to help better accommodate their schedules.

>>>>

---
title: "Investigating Trends of Absences in Toronto City Council Attendance between 2022 to 2026"
subtitle: "Determining the Ideal Meeting Types and Months for the 2022-2026 Term"
author: 
  - Wendy Yuan
thanks: "GitHub repo link: https://github.com/kiwindyy/CityCouncilAttendance"
date: "27 September 2024"
date-format: long
abstract: "This paper looks at trends in absences for Toronto City Council members using data from Open Data Toronto (@toronto-city-council-attendance). The data was used to observe which members had the most absences, absences trends over the years, and what meeting types had the most absences. It was found that evening meetings saw the most absences and absences are predicted to see an increase over the years. Through identifying trends of absences, we can help minimize the number of absences which is important as when City Council members are elected, they are expected to attend meetings to voice the population’s opinions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The data analysis focuses on examining patterns in the data for various causes of absences. It was found that evening meetings experienced the most absences and the trend over the years shows that absences are likely to increase in 2022. Additionally, Michael Thompson, Jaye Robinson, and Vincent Crisanti were found to have the most absences Rather than blaming individuals for absences, understanding these patterns allows for future targeted meeting scheduling to minimize absences. This ensures that elected officials are present to represent the voices of the general.

@@

After importing the data into R (@citeR) using the Open Data Toronto package (@OpenDataToronto), it is cleaned to keep only key variables of interest and make it easier for data analysis in Section 3. To clean the data and produce graphs with the data, the following packages in R (@citeR) were used: tidyverse (@tidyverse), dplyr (@dplyr), lubridate (@lubridate), knitr (@knitr), readr (@readr) and ggplot2 (@ggplot2). ChatGPT (@ChatGPT) was used to help the coding of cleaning, testing, and graphing data.

@@

In @fig-session-member the taller the bar is the more absences that City Council member has had while the opposite is true, the lower the bar the fewer absences. It can be seen that some members rarely miss sessions such as Amber Morley, Olivia Chow, and Paula Fletcher. While Michael Thompson, Jaye Robinson, and Vincent Crisanti have missed many meetings. Thus, @fig-session-member shows a general idea of individual absences, this graph makes it difficult to follow trends in the future.

@@

@fig-session-member from Section 3 laid out the information about the absences of each Toronto City Council member. It can be seen that Michael Thompson has the highest absences, followed by Jaye Robinson and Vincent Crisanti. While Amber Morley, Olivia Chow, and Paula Fletcher have missed few meetings. The variation between members could be problematic especially when the council member fails to represent the population. Additionally, it could suggest differences in engagement, personal schedules, or emergency circumstances. Determining those with the most absences allows steps to be taken to help better accommodate their schedules.
